Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-04-15 Scripts/Initial_Analysis.Rmd
fixed paths on emergence cont.pan

Lon_Lat_DBEM <- read.csv("~/GitHub/TransEmergence/Temporal_Data/Spatial/Lon_Lat_DBEM.txt", header=FALSE)
colnames(Lon_Lat_DBEM) <- c("index","lon","lat")

@@

eez_centroid <- read.csv("~/GitHub/TransEmergence/Temporal_Data/Spatial/eez_centroids.csv", header=TRUE)

>>>>

Lon_Lat_DBEM <- read.csv(paste(data_path,"Spatial/Lon_Lat_DBEM.txt",sep=""), header=FALSE)
colnames(Lon_Lat_DBEM) <- c("index","lon","lat")

@@

eez_centroid <- read.csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""), header=TRUE)
